---
title: "Optimized P_MA list and graphs.pdf"
author: "Tianyu Zhang"
date: "2025-03-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Test for NVDA data
```{r}
library(tseries)
library(zoo)
library(quantmod)
library(TTR)

symbol <- "NVDA"
stock_data <- get.hist.quote(instrument = symbol,
                             start = "2010-01-01",
                             end = "2024-12-31",
                             quote = "AdjClose",
                             compression = "m")
stock_data <- zoo(stock_data, order.by = as.Date(time(stock_data)))
colnames(stock_data) <- "AdjClose"

# MA
ma_short <- rollmean(stock_data$AdjClose, k = 10, fill = NA, align = "right")
ma_long  <- rollmean(stock_data$AdjClose, k = 30, fill = NA, align = "right")
diff_ma  <- scale(ma_short - ma_long)

# DIFF_MA:
plot(diff_ma, type = "l", col = "blue", main = "diff_ma (scaled): NVDA")

```

```{r}
sigma <- function(x) {1 / (1 + exp(-x))}

lambda1 <- 0.1
lambda2 <- 10

p_ma_01 <- sigma(lambda1 * diff_ma)
p_ma_10 <- sigma(lambda2 * diff_ma)

plot(p_ma_01, type = "l", col = "blue", main = "compare NVDA P_MA", ylab = "P_MA")
lines(p_ma_10, col = "red")
legend("topright", legend = c("lambda = 0.1", "lambda = 10"), col = c("blue", "red"), lty = 1)

```
We can see there is a difference between lagre and small lambda, the data is valid, next put a pre-retuning stategy for grid search: 

NOTE: We are using X=pre_T_adaptive(same logic as T_adaptive, but it's a easier version only for one model, T_adaptive is more suitable for hypermodel) for each stocks:  

If the signal (P_MA) is greater than X → Go Long (expecting price to rise)  


If the signal is less than X-0.2 → Go Short (expecting price to fall)  


If the signal is between X-0.2 and X → Hold (no trade; uncertainty zone)  

# Using Grid search oprimazation logic for NVDA:
```{r}
library(tseries)
library(zoo)
library(quantmod)
library(TTR)
library(PerformanceAnalytics)
library(xts)

symbol <- "NVDA"
stock_data <- get.hist.quote(instrument = symbol,
                             start = "2010-01-01",
                             end = "2024-12-31",
                             quote = "AdjClose",
                             compression = "m")
stock_data <- zoo(stock_data, order.by = as.Date(time(stock_data)))
colnames(stock_data) <- "AdjClose"

ma_short <- rollmean(stock_data$AdjClose, k = 12, fill = NA, align = "right")
ma_long  <- rollmean(stock_data$AdjClose, k = 36, fill = NA, align = "right")
diff_ma  <- scale(ma_short - ma_long)

#sigmoid
sigma <- function(x) {1 / (1 + exp(-x))}

# Range for lambda
lambda_values <- seq(0.1, 10, by = 0.1)
score_list <- data.frame()

for (lambda in lambda_values) {
  p_ma <- sigma(lambda * diff_ma)
  valid_index <- which(!is.na(p_ma))
  
  df <- data.frame(Date = index(stock_data)[valid_index],
                   AdjClose = coredata(stock_data$AdjClose)[valid_index],
                   P_MA = coredata(p_ma[valid_index]))
  
  # log return
  returns <- diff(log(df$AdjClose))
  signals <- df$P_MA[-1]

  # Trading logic:
  strategy_returns <- ifelse(signals > 0.46, returns,
                             ifelse(signals < 0.25, -returns, 0))
  strategy_returns <- xts(strategy_returns, order.by = df$Date[-1])

  # This step is for checking the data's sufficiency
  if (length(strategy_returns) < 5 || sd(strategy_returns, na.rm = TRUE) == 0) next

  sharpe <- as.numeric(SharpeRatio.annualized(strategy_returns, scale = 12, geometric = FALSE))
  wins <- sum(strategy_returns > 0, na.rm = TRUE)
  losses <- sum(strategy_returns < 0, na.rm = TRUE)
  win_loss <- ifelse(losses == 0, wins, wins / losses)

  # Keep each sharpe + win_loss score
  score <- sharpe + win_loss
  score_list <- rbind(score_list, data.frame(Lambda = lambda, Sharpe = sharpe, WinLoss = win_loss, Score = score))
}

# Find the best lambda for NVDA:
best_row <- score_list[which.max(score_list$Score), ]
print(score_list)
print(best_row)
```
```{r}
# plot Lambda vs Score
plot(score_list$Lambda, score_list$Score, type = "l", col = "blue",
     main = "Lambda vs Score: NVDA", xlab = "Lambda", ylab = "Score")
points(best_row$Lambda, best_row$Score, col = "red", pch = 19)
legend("topright", legend = paste("Best =", round(best_row$Lambda, 2)), col = "red", pch = 19)

```

# Same logic, put SOXL into the loop:
```{r}
# Same logic, put SOXL into the code:
symbol2 <- "SOXL"
stock_data2 <- get.hist.quote(instrument = symbol2,
                              start = "2010-01-01",
                              end = "2024-12-31",
                              quote = "AdjClose",
                              compression = "m")
stock_data2 <- zoo(stock_data2, order.by = as.Date(time(stock_data2)))
colnames(stock_data2) <- "AdjClose"

ma_short2 <- rollmean(stock_data2$AdjClose, k = 12, fill = NA, align = "right")
ma_long2  <- rollmean(stock_data2$AdjClose, k = 36, fill = NA, align = "right")
diff_ma2  <- scale(ma_short2 - ma_long2)

score_list2 <- data.frame()
for (lambda in lambda_values) {
  p_ma <- sigma(lambda * diff_ma2)
  valid_index <- which(!is.na(p_ma))
  df <- data.frame(Date = index(stock_data2)[valid_index],
                   AdjClose = coredata(stock_data2$AdjClose)[valid_index],
                   P_MA = coredata(p_ma[valid_index]))
  returns <- diff(log(df$AdjClose))
  signals <- df$P_MA[-1]
  strategy_returns <- ifelse(signals > 0.35, returns,
                             ifelse(signals < 0.15, -returns, 0))
  strategy_returns <- xts(strategy_returns, order.by = df$Date[-1])
  if (length(strategy_returns) < 5 || sd(strategy_returns, na.rm = TRUE) == 0) next
  sharpe <- as.numeric(SharpeRatio.annualized(strategy_returns, scale = 12, geometric = FALSE))
  wins <- sum(strategy_returns > 0)
  losses <- sum(strategy_returns < 0)
  win_loss <- ifelse(losses == 0, wins, wins / losses)
  score <- sharpe + win_loss
  score_list2 <- rbind(score_list2, data.frame(Symbol = symbol2, Lambda = lambda, Sharpe = sharpe, WinLoss = win_loss, Score = score))
}
best2 <- score_list2[which.max(score_list2$Score), ]
print(score_list2)
print(best2)

```
```{r}
plot(score_list2$Lambda, score_list2$Score, type = "l", col = "blue",
     main = "Lambda vs Score: SOXL", xlab = "Lambda", ylab = "Score")
points(best2$Lambda, best2$Score, col = "red", pch = 19)
legend("topright", legend = paste("Best =", round(best2$Lambda, 2)), col = "red", pch = 19)

```

# Same logic, put XOM into the loop:
```{r}
symbol3 <- "XOM"
stock_data3 <- get.hist.quote(instrument = symbol3,
                              start = "2010-01-01",
                              end = "2024-12-31",
                              quote = "AdjClose",
                              compression = "m")
stock_data3 <- zoo(stock_data3, order.by = as.Date(time(stock_data3)))
colnames(stock_data3) <- "AdjClose"

ma_short3 <- rollmean(stock_data3$AdjClose, k = 12, fill = NA, align = "right")
ma_long3  <- rollmean(stock_data3$AdjClose, k = 36, fill = NA, align = "right")
diff_ma3  <- scale(ma_short3 - ma_long3)

score_list3 <- data.frame()
for (lambda in lambda_values) {
  p_ma <- sigma(lambda * diff_ma3)
  valid_index <- which(!is.na(p_ma))
  df <- data.frame(Date = index(stock_data3)[valid_index],
                   AdjClose = coredata(stock_data3$AdjClose)[valid_index],
                   P_MA = coredata(p_ma[valid_index]))
  returns <- diff(log(df$AdjClose))
  signals <- df$P_MA[-1]
  strategy_returns <- ifelse(signals > 0.38, returns,
                             ifelse(signals < 0.18, -returns, 0))
  strategy_returns <- xts(strategy_returns, order.by = df$Date[-1])
  if (length(strategy_returns) < 5 || sd(strategy_returns, na.rm = TRUE) == 0) next
  sharpe <- as.numeric(SharpeRatio.annualized(strategy_returns, scale = 12, geometric = FALSE))
  wins <- sum(strategy_returns > 0)
  losses <- sum(strategy_returns < 0)
  win_loss <- ifelse(losses == 0, wins, wins / losses)
  score <- sharpe + win_loss
  score_list3 <- rbind(score_list3, data.frame(Symbol = symbol3, Lambda = lambda, Sharpe = sharpe, WinLoss = win_loss, Score = score))
}
best3 <- score_list3[which.max(score_list3$Score), ]
print(score_list3)
print(best3)
```

```{r}
plot(score_list3$Lambda, score_list3$Score, type = "l", col = "blue",
     main = "Lambda vs Score: XOM", xlab = "Lambda", ylab = "Score")
points(best3$Lambda, best3$Score, col = "red", pch = 19)
legend("topright", legend = paste("Best =", round(best3$Lambda, 2)), col = "red", pch = 19)

```

# Same logic, put CLS.TO into the loop:
```{r}
symbol4 <- "CLS.TO"
stock_data4 <- get.hist.quote(instrument = symbol4,
                              start = "2010-01-01",
                              end = "2024-12-31",
                              quote = "AdjClose",
                              compression = "m")
stock_data4 <- zoo(stock_data4, order.by = as.Date(time(stock_data4)))
colnames(stock_data4) <- "AdjClose"

ma_short4 <- rollmean(stock_data4$AdjClose, k = 12, fill = NA, align = "right")
ma_long4  <- rollmean(stock_data4$AdjClose, k = 36, fill = NA, align = "right")
diff_ma4  <- scale(ma_short4 - ma_long4)

score_list4 <- data.frame()
for (lambda in lambda_values) {
  p_ma <- sigma(lambda * diff_ma4)
  valid_index <- which(!is.na(p_ma))
  df <- data.frame(Date = index(stock_data4)[valid_index],
                   AdjClose = coredata(stock_data4$AdjClose)[valid_index],
                   P_MA = coredata(p_ma[valid_index]))
  returns <- diff(log(df$AdjClose))
  signals <- df$P_MA[-1]
  strategy_returns <- ifelse(signals > 0.49, returns,
                             ifelse(signals < 0.29, -returns, 0))
  strategy_returns <- xts(strategy_returns, order.by = df$Date[-1])
  if (length(strategy_returns) < 5 || sd(strategy_returns, na.rm = TRUE) == 0) next
  sharpe <- as.numeric(SharpeRatio.annualized(strategy_returns, scale = 12, geometric = FALSE))
  wins <- sum(strategy_returns > 0)
  losses <- sum(strategy_returns < 0)
  win_loss <- ifelse(losses == 0, wins, wins / losses)
  score <- sharpe + win_loss
  score_list4 <- rbind(score_list4, data.frame(Symbol = symbol4, Lambda = lambda, Sharpe = sharpe, WinLoss = win_loss, Score = score))
}
best4 <- score_list4[which.max(score_list4$Score), ]
print(score_list4)
print(best4)
```

```{r}
plot(score_list4$Lambda, score_list4$Score, type = "l", col = "blue",
     main = "Lambda vs Score: CLS.TO", xlab = "Lambda", ylab = "Score")
points(best4$Lambda, best4$Score, col = "red", pch = 19)
legend("topright", legend = paste("Best =", round(best4$Lambda, 2)), col = "red", pch = 19)

```
# Put a list of all stocks' P_MA:
```{r}
# Function of P_MA with best lambda:
get_pma <- function(stock_data, lambda, short_k = 12, long_k = 36) {
  ma_short <- rollmean(stock_data$AdjClose, k = short_k, fill = NA, align = "right")
  ma_long  <- rollmean(stock_data$AdjClose, k = long_k, fill = NA, align = "right")
  diff_ma  <- scale(ma_short - ma_long)
  p_ma <- 1 / (1 + exp(-lambda * diff_ma))
  return(p_ma)
}

# take best lambda:
p_ma_nvda <- get_pma(stock_data,     lambda = 0.1)  # NVDA
p_ma_soxl <- get_pma(stock_data2,    lambda = 0.1)  # SOXL
p_ma_xom  <- get_pma(stock_data3,    lambda = 1.9)  # XOM
p_ma_cls  <- get_pma(stock_data4,    lambda = 0.6)  # CLS.TO

pma_list <- list(
  "CLS.TO" = p_ma_cls,
  "NVDA"   = p_ma_nvda,
  "XOM"    = p_ma_xom,
  "SOXL"   = p_ma_soxl
)

library(knitr)

# Check the tail of each stocks:
tail_df <- data.frame(
  Date    = tail(index(stock_data)),
  NVDA    = tail(na.omit(p_ma_nvda)),
  SOXL    = tail(na.omit(p_ma_soxl)),
  XOM     = tail(na.omit(p_ma_xom)),
  CLS.TO  = tail(na.omit(p_ma_cls))
)

kable(tail_df, caption = "Tail of P_MA for Each Stock (Last 6 Months)")
```


